Latitudinal gradients in biotic niche breadth vary across ecosystem types

### 2018-09-04 manuscript/correction.tex
reformatted correction letter following DBS comments

    We have corrected these inconsistencies and repeated our analyses to ensure that our conclusions did not change. After re-analysis, our results were qualitatively identical to those originally published and our original conclusions hold. However, the specific values for correlations and scaling relationships given in the original results and discussion are incorrect. Below, we present the results section and the last paragraph of the discussion (the only portion to require correction) with corrected values in bold. The original and corrected values may be compared in Tables~\ref{corr_comparison} and~\ref{beta_comparison}. We also show the original and corrected Figures 2-3.  All supplemental figures have also been updated; as with the main-text figures below, any differences were minor. Reference numbers are as in the original main text.

@@

  Importantly, while terrestrial communities are also strongly seasonal at
  high latitudes and can receive significant allochthonous
  inputs [46], terrestrial consumers tend to be
  morphologically specialised for feeding on particular prey [53].
  This means that primarily gape-limited aquatic consumers tend to be more
  generalist across all types of aquatic habitats than terrestrial 
  consumers [5, 53]. This trend also held in our data, although the difference between generality was not significant \textbf{(
    $\mu_{Aquatic}$=5.86, $\mu_{Terrestrial}$=3.75; $p$\textless0.001 for 
    $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$; Table~\ref{corr_comparison})}. 
  The key to this argument is therefore whether freshwater ecosystems experience
  more severe seasonal variation than marine and estuarine ecosystems. Although
  we are not aware of any study explicitly comparing seasonal variation in
  fresh and saltwater ecosystems at similar latitudes, we believe that freshwater 
  ecosystems are indeed likely to experience more severe changes because of their small size.
  While oceans and estuaries certainly vary in terms of water temperature and
  nutrients over the course of a year [51], these changes are likely to be slower
  and milder than in freshwaters because marine and estuarine communities are buffered 
  by being open to the ocean rather than isolated in the midst of a terrestrial matrix. 
  Supporting this hypothesis, net primary productivity is much more variable over the course of a year 
  in non-marine communities [11]. Thus suggests that niche breadths may also be 
  more variable over the course of the year.

>>>>

    We have corrected these inconsistencies and repeated our analyses to ensure that our conclusions did not change. After re-analysis, our results were qualitatively identical to those originally published and our original conclusions hold. However, the specific values for correlations and scaling relationships given in the original results and discussion are incorrect. Below, we present the results section and the beginning of the last paragraph of the discussion (the only portion to require correction). All corrections are highlighted in bold. The original and corrected values may be compared in Tables~\ref{corr_comparison} and~\ref{beta_comparison}. We also show the original and corrected Figures 2-3.  All supplemental figures have also been updated; as with the main-text figures below, any differences were minor. Reference numbers are as in the original main text.

@@

  Importantly, while terrestrial communities are also strongly seasonal at
  high latitudes and can receive significant allochthonous
  inputs [46], terrestrial consumers tend to be
  morphologically specialised for feeding on particular prey [53].
  This means that primarily gape-limited aquatic consumers tend to be more
  generalist across all types of aquatic habitats than terrestrial 
  consumers [5, 53]. This trend also held in our data, although the difference between generality was not significant \textbf{(
    $\mu_{Aquatic}$=5.86, $\mu_{Terrestrial}$=3.75; $p$\textless0.001 for 
    $\mu_{Aquatic}$\textgreater$\mu_{Terrestrial}$; Table~\ref{corr_comparison})}. 
  The key to this argument is therefore whether freshwater ecosystems experience
  more severe seasonal variation than marine and estuarine ecosystems.
